---
title: "Homework Template"
output:
  html_document: default
  pdf_document: default
date: "2023-10-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tinytex)
library(ggplot2)
library(palmerpenguins)
library(janitor)
library(dplyr)
library(tidyverse)
library(png)
```


## QUESTION 01: Data Visualisation for Science Communication

*Create a figure using the Palmer Penguin dataset that is correct but badly communicates the data. **Do not make a boxplot**.*

### a) Provide your figure here:

```{r bad figure code, echo=FALSE}
#here i create the bad plot - a scatterplot that shows flipper length and body mass
data("penguins")
badscatter<- ggplot(penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 5) + 
  labs(title = "Flipper Length and Body Mass", 
       x = "Flipper Length", 
       y = "Body Mass") +
  theme_minimal()

badscatter
```

### b) Write about how your design choices mislead the reader about the underlying data (200-300 words).

*Include references.*

Here, I plotted a scatterplot showing the relationship between flipper length and body mass. There are a number of bad design choices here - firstly, the title poorly describes the data, and the axis labels do not provide any units. This is already a poor start, given that it gives little information about the magnitude of the data and the relationship shown. The points are also extremely large, meaning they overlap eachother and hide data-points, exacerbated by them being opaque. Finally, the points show every species of penguin, with no differentiation between the species. The lack of trend line and confidence interval also makes it difficult to see significant trends. There could even be three trend lines, one for each species to see if the correlation holds true for each, which is unclear currently. 

------------------------------------------------------------------------

## QUESTION 2: Data Pipeline

*Write a data analysis pipeline in your .rmd RMarkdown file. You should be aiming to write a clear explanation of the steps, the figures visible, as well as clear code.*

*Your code should include the steps practiced in the lab session:*

------------------------------------------------------------------------

### Introduction

I am going to investigate whether there is a significant relationship between body mass and flipper length for adelie penguins. I am going to clean the data, plot a clear graph of this data and then move on to perform a pearsons correlation test to see if it is significant. 

The first chunk of code cleans the data, and plots a graph.

```{r Data Exploration}
#so here, I source my file with the preset cleaning functions
source("REPRODUCIBLE_FIGURES/cleaningfunctions/cleaning.R") 
#and then load the data
data("penguins")

#this pipeline cleans my data, removing NA values, and filtering by the species I focus on
penguins_clean <- penguins%>%
  remove_NA() %>%
clean_column_names() %>%
filter_by_species("Adelie") 

#checking the data
head(penguins_clean)

#time to make a figure
goodscatter<- ggplot(penguins_clean, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 2, alpha = 0.5) + 
  labs(title = "Correlation between Flipper Length and Body Mass in Adelie Penguins ", 
       x = "Flipper Length", 
       y = "Body Mass") 


goodscatter

# Save the plot to the subfolder
ggsave(filename = paste0("REPRODUCIBLE_FIGURES/plots", "/goodscatter.pdf"), plot = goodscatter)
```

### Hypothesis

Here I am testing whether there is a correlation between the variables. Ill use a pearson correlation coefficient and a hypothesis test. 
- Null Hypothesis - the observed correlation is NOT significantly different from zero
- Alternative Hypothesis - the observed correlation IS significantly different from zero

This chunk of code runs the simple test.


### Statistical Methods

```{r Statistics}
#Pearson correlation coefficient
correlation<- cor.test(penguins_clean$flipper_length, penguins_clean$body_mass)

print(correlation)
```

### Results & Discussion

Here, the correlation is shown to be 0.4648539, which is positive. The p value is hugely lower than 0.05, our chosen significance level, so we can safely reject the null hypothesis and conclude that there is a significant positive correlation between the two variables.

```{r Plotting Results}

#here I plot my graph again, including a regression line
regressionscatter<- ggplot(penguins_clean, aes(x = flipper_length, y = body_mass)) +
  geom_point(size = 2, alpha = 0.5) + 
  labs(title = "Correlation between Flipper Length and Body Mass in Adelie Penguins ", 
       x = "Flipper Length", 
       y = "Body Mass")  +
  geom_smooth(method = "lm")

```

### Conclusion

Therefore, I can conclude that For Adelie penguins, as they grow heavier, they also are more likely to have longer flippers.
------------------------------------------------------------------------

## QUESTION 3: Open Science

### a) GitHub

*Upload your RProject you created for **Question 2** and any files and subfolders used to GitHub. Do not include any identifiers such as your name. Make sure your GitHub repo is public.*

*GitHub link :https://github.com/panda-anon/ReproducibleFiguresAP*

### b) Share your repo with a partner, download, and try to run their data pipeline.

*Partner's GitHub link:*


### c) Reflect on your experience running their code. (300-500 words)


### d) Reflect on your own code based on your experience with your partner's code and their review of yours. (300-500 words)

-   *What improvements did they suggest, and do you agree?*

-   *What did you learn about writing code for other people?*
